%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
\hyphenpenalty=10000
%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\huge{Rushabh Gala} \\[3pt]
\href{https://github.com/rushabhgala}{\raisebox{-0.05\height}\faGithub\ rushabhgala} \ $|$ \ 
\href{https://linkedin.com/in/rushabh-gala-b680b4149/}{\raisebox{-0.05\height}\faLinkedin\ rushabh-gala-b680b4149} \ $|$ \ 
%\href{https://rushabh.space}{\raisebox{-0.05\height}\faGlobe \ Website} \ $|$ \ 
\href{mailto:rngala@ncsu.edu}{\raisebox{-0.05\height}\faEnvelope \ rngala@ncsu.edu} \\ 
%\href{tel:+1-919-633-6594}{\raisebox{-0.05\height}\faMobile \ +1-919-633-6594} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
%\section{Summary}
%Experienced data analyst with a strong background in large-scale data analysis, visualization, modeling, and Monte Carlo simulations. Proficient in interpreting complex datasets and communicating findings to diverse audiences.
%Experienced data analyst proficient in conducting independent research, with a strong track record of delivering insightful findings and solutions. Skilled in analyzing large datasets, employing sophisticated modeling techniques, and communicating results effectively to diverse audiences.
%Experience
\section{Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{North Carolina State University} & Raleigh, NC \hfill 2018 - Present \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt]
\item[--] \textbf{Led data analysis and modeling} efforts to understand background radiation patterns for the LEGEND experiment, resulting in a significant contamination reduction by a \textbf{factor of 100}. Presented findings at national and international conferences, contributing to the advancement of nuclear physics research.
\item[--] Utilized \textbf{statistical techniques}, including \textbf{Bayesian statistics}, to perform intricate simulations and analyze large datasets, maximizing Poissonian likelihood functions. Presented results at the prestigious TAUP-2023 conference, receiving recognition for groundbreaking research.
\item[--] \textbf{Developed custom software} in C++ to calculate photon detection probabilities in a light-sensitive SiPM detector, originating from radioactive decays in Liquid Argon. The software facilitated precise experimental planning and analysis, ensuring accurate results.
\item[--] \textbf{Planned, developed, and executed} a Geant4-based custom software to build a complex system with more than 1000 detectors with mm precision. Conducted precise Monte Carlo simulations of radioactive decays to determine radioactive contamination and performed rigorous analysis to meet the ambitious objective of achieving \textbf{$<$ 1 count of background noise in 10 years of data}.
\item[--] Implemented \textbf{regression and non-linear fitting} methods to estimate the age of Brazil nuts using radioactive decay techniques, achieving a remarkable 5\% error margin. Published results in peer-reviewed journals, showcasing scientific rigor and expertise.
\item[--] Developed sophisticated Python and C++ tools to meticulously design the layout of detectors, optical fibers, and ancillary materials for our experiment. Collaborated closely with the engineering team to define spatial constraints, ensuring seamless integration.
\item[--] Provided \textbf{expert guidance} on data analysis and interpretation to a student investigating simulation efficiency differences between CAD-based and solid-based geometry implementations in Geant4. The results of our collaboration were pivotal in determining the optimal approach for future simulations, significantly enhancing experimental efficiency and accuracy.
\end{itemize}
\end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Tata Institute of Fundamental Research} & Mumbai, India \hfill 2017 - 2018 \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt]
\item[--] Conducted in-depth \textbf{data analysis} of experimental results from an accelerator-based experiment, leading to the discovery of novel energy levels in the $^{90}Zr$ nucleus. Published findings in renowned scientific journals, contributing significantly to the field of nuclear physics.
\item[--] Implemented \textbf{advanced non-linear fitting techniques} to determine the lifetime of an isomeric state using slow-fast coincidence methodology. Managed large datasets with meticulous attention to detail, ensuring accurate results and data integrity.
\item[--] Optimized the voltage response of semiconductor and plastic detectors, improving energy resolution by \textbf{10\%} and enhancing experimental precision. Presented research findings at national and international conferences, receiving accolades for outstanding contributions to the field.
\item[--] Delivered an engaging \textbf{oral presentation} and won a prestigious \textbf{first prize} at the Science Academies’ Refresher’s Course on Mathematical Physics, showcasing exemplary communication and presentation skills.
\end{itemize}
\end{minipage}
}
\end{tabularx}
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Relevant Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Skills &  \normalsize{C++, Python, Bash, Julia, Mathematica}\\
Technical Skills & \normalsize{Linux, Git, Docker, JSON, snakemake Office Suite, Tableau, Grid computing}\\
%Technical Skills  &  \normalsize{Data analysis, modeling, visualization, and presentation}\\
Interpersonal Skills  &  \normalsize{Course Instructor : Undergraduate physics courses, APS Student Ambassador, Events Head: Indian Graduate Student Association, Public Relations Team}
\end{tabularx}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
PhD in Physics & \textbf{NC State University} \hfill 2018-Present \\
Master's in Physics & \textbf{University of Mumbai} \hfill 2015-2017 \\ 
Bachelor's in Physics & \textbf{Ramnarain Ruia College} \hfill  2012-2015 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Selected Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}
\vfill

\end{document}
